---
output: github_document
---

```{r, include = FALSE}
pkgload::load_all(export_all = FALSE, helpers = FALSE)
knitr::opts_chunk$set(
  collapse = TRUE,
  cache = !TRUE,
  comment = "#>",
  message = FALSE, 
  warning = FALSE, 
  out.width = "100%",
  fig.align = "center",
  fig.width = 8,
  fig.path = "inst/figures/"
)
```

# __db.censusnz__ (censusnz database plugin)

<!-- badges: start -->
[![pipeline-status](https://gitlab.harmonic.co.nz/harmonic/databases/db-censusnz/badges/master/pipeline.svg)](https://gitlab.harmonic.co.nz/harmonic/databases/db-censusnz/)
[![coverage-status](https://gitlab.harmonic.co.nz/harmonic/databases/db-censusnz/badges/master/coverage.svg?job=coverage)](https://gitlab.harmonic.co.nz/harmonic/databases/db-censusnz/pipelines)
<!-- badges: end -->

A way to access the 2018 NZ Census Data. This package includes datasets of
census responses grouped by different geographic areas.

In future, functions to help access the data will also exist.

## Installation

To install this package from gitlab, you must first generate a Personal Access
Token; the package can then be installed using via the Remotes package:

```r
Sys.setenv(GITLAB_PAT = "xxxxxxxxxxxxxxxxxxxx")
remotes::install_gitlab(repo = 'harmonic/packages/censusnz', host = 'gitlab.harmonic.co.nz/')
remotes::install_gitlab(repo = 'harmonic/databases/db-censusnz', host = 'gitlab.harmonic.co.nz/')
```

Alternatively the `utilic` package can be used:

```r
utilic::install_harmonic('harmonic/packages/censusnz')
utilic::install_harmonic('harmonic/databases/db-censusnz')
```

---

# Basic Usage of `db.censusnz`

```{r child = 'vignettes/basic-usage.Rmd'}
```

